Fast algebraic filtering of surfaces from 3D medical images with Julia

### 2019-07-06 src/examples.tex
new examples

@@

>>>>

The size of boundary matrix is critical parameter of LAR-SURF method. To determine optimal size of boundary matrix the experiment on artifical data was performed (Fig.  \ref{fig:bm_size_tesla}). Size of experimental data is set to $512\times512\times512$ and it is derived from typical size of Computed Tomography medical images. Computation is done on Tesla DGX-1 machine

\begin{figure}
\includegraphics[width=0.99\textwidth]{figs/bm_size_tesla.pdf} 
%\includegraphics[scale=1]{input/ircad_comparison.pdf} 
\caption{Time requirements of LAR-SURF filter used on artifical with different size of boundary matrix}
\label{fig:bm_size_tesla}
\end{figure}

@@

We performed experiment on Ircad dataset to compare time requirements and used t-test  check the  Based on $\alpha=0.99$ the with the $p=\input{input/ircad_pvalue}$ , 
$s=\input{input/ircad_statistics}$

\begin{figure}
\includegraphics[width=0.99\textwidth]{figs/ircad_comparison.pdf} 
%\includegraphics[scale=1]{input/ircad_comparison.pdf} 
\caption{Time requirements of LAR-SURF filter and Marching Cubes on Ircad dataset. Error bars shows the 95\% confidence interval}
\label{fig:ircad_comparison}
\end{figure}
